upwell_IDX

### 2019-08-13 upwell_IDX.Rmd
Tweaking

```{r}
library(tidyverse)
library(ggplot2)
library(circular)
# devtools::install_github("robwschlegel/coastR")
library(coastR)
library(gridExtra)
library(dplyr)
library(geosphere)
library(heatwaveR)
```

@@

```{r}
load("Data/wind_daily.RData") 
wind_daily <- wind_daily %>% 
  dplyr::rename(sites = temp_sites)
```

@@

# Exceedence function heatwaveR - This is done to determine the consecutive number of days at or above what the UI value is ment to be

@@

SACTN_upwell <- SACTN_US %>% 
  dplyr::rename(t = date) %>%
  group_by(site) %>%
  nest() %>% 
  mutate(exceed = purrr::map(data, exceedance, threshold = 12.4, below = TRUE))

>>>>

```{r}
library(tidyverse)
library(circular)
# devtools::install_github("robwschlegel/coastR")
library(coastR)
library(gridExtra)
library(geosphere)
library(heatwaveR)
```

@@

```{r}
load("Data/wind_daily.RData") 
wind_daily <- wind_daily %>% 
  dplyr::rename(sites = temp_sites)
load("Data/site_list_sub.Rdata")
```

@@

# Exceedence function heatwaveR - This is done to determine the consecutive number of days at or above what the UI value is meant to be

@@

SACTN_upwell <- UI_angle %>% 
  dplyr::rename(t = date,
                temp = ui.saws) %>%
  group_by(site) %>%
  # mutate(min_t = min(t), 
  #        max_t = max(t)) %>% 
  nest() %>% 
  mutate(clim = purrr::map(data, ts2clm, climatologyPeriod = c("2000-01-01", "2005-12-31")),
         exceed = purrr::map(clim, exceedance, minDuration = 3, threshold = 3)) %>% 
  # mutate() %>% 
  select(-data, -clim) %>% 
  unnest()
